Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain body_limit
Explain empty_second_line

\subsubsection{body_limit}
\label{subs:body_limit}

\subsubsection{empty_second_line}
\label{subs:empty_second_line}

>>>>

\subsubsection{body_limit}
\label{subs:body_limit}
The lines of the body should be limited to 72 characters (originally stated in \cite{TP}). As with the subject line limit, this ensures proper display of the (full) commit message with limited space available. The test on this criterion will be undefined if no body is used.

\subsubsection{empty_second_line}
\label{subs:empty_second_line}
The subject line and the body should be separated by an empty line (\cite{TP}). This is how programs (including git itself) parsing the commit message which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial. If no body is used, the test on this criterion will be undefined.
